---
title: "FCAT Euro2020 Sweep"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

seed = 75229
```

Welcome to the FCAT Euro2020 Sweep! Your chance to add a little spice to your
summer and maybe win a valuable Cash[^1] Prize! As usual there are a range of
prizes available to maximise the chances of prolonging your interest.

- **Winner** receives £10 worth of FCAT fun points
- **Runner up** gets £5

In addition there are some bonus categories with a value of £3 each:

- **Wooden Spoon** for the worst team in the tournament based on results
- **Entertainers** for the team that scores the most goals
- **Thugs** for the team with the most red and yellow cards

All statistics will be drawn from the official
[Euro2020](https://www.uefa.com/uefaeuro-2020/) website. The organisers reserve
the right to tweak the criteria for the bonus categories, to break ties or
generally to keep it sensible. As always in case of questions over the rules,
the organisers decision is _final_.

[^1]: Well, not real cash since we are not collecting stake money. But you will
get a warm fuzzy feeling inside.

## The draw

The draw has been conducted in a rigorously reproducible manner, seeded with a
random number. The random seed used, _`r format(seed, digits = 3)`_, was
generated by Maria, Matt, Michael, Nick and Nina in the FCAT meeting on 9^th^
June: blame them. The code to reproduce it is below.

```{r sweep, message=FALSE}
library(tibble)
library(dplyr)

names <- c("Michael Archer", "Matthew Bardrick", "Nick Boase", "Zoe Donkin",
           "Luke Hamilton", "Catharine Hammond", "Eleanor Harris", "Courtney Keane", 
           "Jenny Kemp", "George Koutsoumanis", "David Lee", "Nafisa Mathia", 
           "Molly O'Connor", "Maria Prokopiou", "Nina Sal", "Andrew Scaife",
           "Barsha Sharma", "Christopher Silwood", "Jonathan Smith", "Isabella Worth",
           "Shak Shah", "Ian Lonsdale", "Marcia Bogle", "Tom Powell")  

countries <- c("Italy", "Switzerland", "Turkey", "Wales",
               "Belgium", "Russia", "Denmark", "Finland",
               "Ukraine", "Netherlands", "Austria", "North Macedonia",
               "England", "Croatia", "Czech Republic", "Scotland",
               "Spain", "Poland", "Sweden", "Slovakia", 
               "Germany", "France", "Portugal", "Hungary")

seed = 75229
set.seed(seed)
draw <- tibble(country = sample(countries), name = names) %>% 
  arrange(country)

knitr::kable(draw)

```


## The tournament

I will add some data in here, once:

1. I have some data
2. Ive figured out how to wrangle it

```{r groups, echo=FALSE, message=FALSE}

teams <- data.frame(
  country=c("Turkey", "Italy", "Wales", "Switzerland",
            "Denmark", "Finland", "Belgium", "Russia",
            "Netherlands", "Ukraine", "Austria", "North Macedonia",
            "England", "Croatia", "Scotland", "Czech Republic",
            "Spain", "Sweden", "Poland", "Slovakia",
            "Hungary", "Portugal", "France", "Germany"),
  group=rep(LETTERS[1:6], each=4)) %>% 
  left_join(draw)

```




```{r sessioninfo}
sessionInfo()
```